Modal type theory based on the intuitionistic epistemic logic

### 2018-02-10 article.tex
fixes

By default we will consider a strong functor on cartesian closed category with $\eta$ \cite{Cons}.

>>>>

By default we will consider some strong lax monoidal functor on cartesian closed category.

Note that lax monoidal functor on a cartesian closed category is a special case of an applicative functor \cite{Cons}, but
we will define $\eta$ explicitly for simplicity.
